Spatial Reasoning and Statistical Graphics

### 2014-11-02 Paper/Draft1/TestingVisualAptitude.Rnw
added linear model

\end{document}

>>>>

<<linearmodel, results='hide'>>=
ans.model <- data.frame(ans.summary, data.frame(pca2$x))
# exclude all variables that are not supposed to go into the linear model
# those are the unrotated tests; instead we have the PCs
excl <- c("id", "card_rot", "fig_class", "folding", "vis_search", "vidgame_hrs", "major1", "major2", "minor1", "minor2", "learning_disability", "colorblind", "epilepsy", "normal_vision")

ans.model$math_science_research <- ans.model$math_science_research=="y"
ans.model$stats_class <- ans.model$stats_class=="y"
ans.model$calc_1 <- ans.model$calc_1=="y"
pcmath <- prcomp(ans.model[,c("math_science_research", "stats_class", "calc_1", "math_skills")])
biplot(pcmath)
biplot(pcmath, 3:4)
# variables split into stats_class/math_science_research and calc_1/math_skills
# leave out math_skills in favor of calc_1 - for interpretability

xtabs(~stats_class+math_science_research, data=ans.model)
# only one kid is doing research without a stats class
# recode to sum of them
ans.model$statsP <- with(ans.model, stats_class + math_science_research)

excl <- c(excl, c("math_skills", "math_science_research", "stats_class"))
incl <- setdiff(names(ans.model), excl)

m0 <- lm(lineup~., data=ans.model[, incl])

# use AIC in backward selection
library(MASS)
m1 <- stepAIC(m0, direction="both")
@
<<modelresults>>=
anova(m1)
summary(m1)
@
\end{document}
